Cluster Paper

### 2015-03-30 ms.tex
added a bit to the mass section

\subsection{Dynamical Properties}
The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem. At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs. The most commonly used estimate is the corrected sample standard deviation, given by:
\begin{equation}
	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
\end{equation}
with $\{x_1, x_2, ..., x_n\}$ is the random sample and $\bar{x}$ is the sample mean. The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn. An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be \textit{robust}.

@@

\editorial{Need to talk about how the new biweight is different. Also need to talk about how we are using DM halos and not galaxies, so we are only going to do so well when comparing the 3d dispersions and the dispersions that we are calculating.}

For the mass \editorial{Following \cite{Evrard2008, VanderBurg2014, Sifon2013}}.

>>>>

\subsection{Dynamical Properties}
\subsubsection{Velocity Dispersion}
The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem. At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs. The most commonly used estimate is the corrected sample standard deviation, given by:
\begin{equation}
	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
\end{equation}
with $\{x_1, x_2, ..., x_n\}$ is the random sample and $\bar{x}$ is the sample mean. The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn. An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be \textit{robust}.

@@

\editorial{Need to talk about how the new biweight is different. Also need to talk about how we are using DM halos and not galaxies, so we are only going to do so well when comparing the 3d dispersions and the dispersions that we are calculating. Evrard2008 does a good job explaining the DM-galaxy bias we are assuming it is 1}

\subsubsection{Dynamical Mass}
Recently, the relationship between the velocity dispersion and dynamical mass has been the focus of several studies (\eg, \citealt{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}), and find a best-fitting relation for the mass enclosed by $r_{200c}$ of the form
\begin{equation}
	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{\sigma_{15}} \bigg{)}^{-\alpha} \Msol
\end{equation}
where $\sigma_{15} = 1082.9 \pm 4.0 \kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0 \sqrt{\Omega_\Lambda + (1+z)^3\Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies.
